\documentclass[letterpaper,10.5pt]{article}
\include{header}

\begin{document}
\begin{center}
    \Huge{\textbf{Jad F. Alaoui}}

    \begin{itemize*}
        \item[] \href{https://linkedin.com/in/jadalaoui}{linkedin.com/in/jadalaoui}
        \item \href{mailto:alaoui@umich.edu}{alaoui@umich.edu}
        \item \href{tel:+17348642590}{(734) 864-2590}
    \end{itemize*}
\end{center}

\section{Education}
\subheading{University of Michigan}{}{August 2022 - April 2026}
{B.S.E. in Computer Science, Minor in Business}{Ann Arbor, MI}
\begin{itemize}
    \item \textbf{CS Coursework}: Computer Vision, Software Engineering, User Interface Development, Data Structures and Algorithms, Discrete Mathematics, Machine
          Learning, Algorithm and Computation Theory, Computer Organization, Command-Line Interfaces
    \item \textbf{Honors and Extracurriculars}: College of Engineering Dean's List, Traders at Michigan, Michigan Hackers, ITS-Michigan
\end{itemize}

\section{Experience}
\subheading{FedEx}{}{June -- August 2024}
{Software Engineer, Internship}{Miami, FL}
\begin{itemize}
    \item Supported the Central Planning \& Engineering team in developing and implementing data migration strategies, automating processes to streamline operations, improve decision-making, and drive multiple strategic initiatives in Operations Technology \& Analytics.
    
    \item Contributed to the development and implementation of advanced forecasting algorithms and machine learning solutions in the Latin American \& Caribbean region, aimed at improving efficiency, optimizing costs, and advancing the company's goals in the region.
\end{itemize}


\subheading{Ineos}{}{June -- August 2023}
{Software Engineer, Internship}{Remote}
\begin{itemize}
    \item Spearheaded development of an internal inventory tool to track laptops within the office environment, utilizing Python, SQLite, and the Django framework. Tailored the tool to specific requirements and met company standards in terms of security and accessibility.
    
    \item Designed and deployed an internally hosted web application, to streamline the process of tracking and assigning company-issued property. This tool, still in active use, has improved asset management and allocation efficiency throughout the company.
\end{itemize}

\subheading{Casablanca Stock Exchange}{}{June -- August 2022}
{Software Engineer, Internship}{Casablanca, Morocco}
\begin{itemize}
    \item Cooperated with the Information Systems team to facilitate the stock exchange’s transition to online trading. Contributed to the implementation of solutions that reduced operation processing time by 40\%, decreasing trading latency between banks and the exchange.
    
    \item Organized focus groups involving the C-Suite and led by the CEO, centered around retail trading's future in Morocco. Analyzed market trends and regulatory considerations, gaining insight into the financial industry's impact on the local economy.
\end{itemize}
\subheading{Nokia}{}{June -- July 2021}
{Software Engineer, Internship}{Remote}
\begin{itemize}
    \item Collaborated with sales and logistics teams to develop Python scripts, optimizing tasks such as customer support and network optimization. Gained hands-on experience in scripting and problem-solving, through process automation and optimization.
    
    \item Participated in network planning projects across Africa, shadowing key executives. Compiled valuable insights into network infrastructure, strategic planning, and cross-functional collaboration into a detailed, peer-reviewed report on global telecom operations.

\end{itemize}

\section{Projects}
\subheading{Bon Voyage}{}{April -- May 2024}
{Django, RESTful APIs, AJAX, Google Gemini}{Created for MHacks X Google Hackathon}
\begin{itemize}
    \item Developed a Django-based travel planning tool integrating Skyscanner and Google Gemini 1.5 Pro to automate personalized travel suggestions, integrating flight and hotel recommendations, and boosting data handling and application responsiveness through AJAX.
    \item Tackled technical challenges such as API rate limiting and complex data parsing, advancing our team's expertise in machine learning and collaborative software development. Deployed on a serverless environment, allowing for inexpensive low-latency processing.
\end{itemize}
\subheading{Zingers Trading Simulator}{}{January -- April 2024}{Python, Django, SQL, REST, React, Tailwind}{Created for Traders at Michigan}
\begin{itemize}
    \item Engineered a web-based trading simulator project using Python, Django, React, and Tailwind CSS, emphasizing secure user authentication, real-time trading mechanics, and an engaging UI for an immersive learning experience in market trading dynamics.
    
    \item Designed RESTful APIs for dynamic portfolio management, implemented websocket-based live market updates, and utilized Django models with SQLite for price tracking and leaderboard updates, enhancing user engagement through competitive learning.
\end{itemize}
\section{Skills}
\textbf{Technical Languages}: Python, C/C++, MATLAB, Java, JavaScript/TypeScript, HTML/CSS,
SQL (SQLite), R, \LaTeX \\
\textbf{Tools}: Git, Jupyter Notebook, Django, Magento, Adobe Creative Suite, VMWare, LangChain, PowerBI, Streamlit \\
\textbf{Languages}: English, French, Arabic, Spanish
\end{document}
